gtrends_cleaning

### 2022-03-01 paper1-cleaning.Rmd
Finish initial findings

vacc_hes_gtrends <- find_cross_sectional_trends(c('covid conspiracy',
                                                  'COVID-19 vaccine',
                                                  'Coronavirus',
                                                  'Covid-19'
                                                  # URLdecode('%2Fg%2F11j8_9sv06'),
                                                  # URLdecode('%2Fg%2F11j2cc_qll')
                                                  ), 
                            '2021-05-26', 12) %>%   
  pivot_wider(names_from = keyword, values_from = hits)  %>% 
  select(-date) %>% 
  janitor::clean_names()

vacc_hes <- vacc_hes_data %>% 
  left_join(select(dma, FIPS, DMA_google), by = c('fips' = 'FIPS')) %>% 
  full_join(vacc_hes_gtrends, by = c('DMA_google' = 'location'))

vacc_hes %>% 
  pivot_longer(cols = covid_conspiracy:covid_19) %>% 
  ggplot(aes(y = vacc_hesitant, x = value, color = name)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "lm") +
  facet_wrap(~ name)

@@

mask_gtrends <- find_cross_sectional_trends(c('Face mask',
                                              'Mask',
                                              'Cloth face mask'
                                              ),
                                            '2020-07-02', 12)%>%   
  pivot_wider(names_from = keyword, values_from = hits)  %>% 
  select(-date) %>% 
  janitor::clean_names()

mask <- mask_data %>% 
  left_join(select(dma, FIPS, DMA_google), by = c('fips' = 'FIPS')) %>% 
  full_join(mask_gtrends, by = c('DMA_google' = 'location'))

mask %>% 
  pivot_longer(cols = face_mask:civil_and_political_rights) %>% 
  ggplot(aes(y = mask_rare, x = value, color = name)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "lm") +
  facet_wrap(~ name)

@@

append_years <- function(year_begin, year_end){
  years <- seq(year_begin,year_end,1)
  results <- tibble('location' = character(),
    'suicide' = numeric(), 
    'depression' = numeric(),
    'suicide hotline' = numeric(),
    'year' = numeric()
    )
  for (i in years){
    print(glue("finding trends for {i}..."))
    results <- find_cross_sectional_trends(c('suicide', 'depression', 'suicide hotline'),
                                glue("{i}-01-01"), 365) %>%
      pivot_wider(names_from = keyword, values_from = hits)  %>%
      select(-date) %>%
      mutate(year = i) %>% 
      bind_rows(results)
  }
  results
}

suicide_gtrends <- append_years(2010, 2020)

suicide <- suicide_measures %>% 
  left_join(select(dma, FIPS, DMA_google), by = c('fips' = 'FIPS')) %>% 
  full_join(suicide_gtrends, by = c('DMA_google' = 'location', 'year' = 'year'))  %>% 
  janitor::clean_names()

suicide <- suicide %>% 
  group_by(fips) %>%
  mutate(deaths           = na.approx(deaths, na.rm = FALSE),
         population       = na.approx(population, na.rm = FALSE),
         suicide          = na.approx(suicide, na.rm = FALSE),
         depression       = na.approx(depression, na.rm = FALSE),
         suicide_hotline  = na.approx(suicide_hotline, na.rm = FALSE))

@@

suicide <- suicide %>% 
  left_join(county, by = c('fips', 'year'))

write_rds(suicide, here('data', 'cleaned_data', 'suicide.rds'))

@@

pres_2020_gtrend <- find_cross_sectional_trends(c('Joe Biden', 'Donald Trump'), '2020-01-01', 307) %>% 
  pivot_wider(names_from = keyword, values_from = hits)  %>% 
  select(-date)

pres_2016_gtrend <- find_cross_sectional_trends(c('Hilary Clinton', 'Donald Trump'), '2016-01-01', 307) %>% 
  pivot_wider(names_from = keyword, values_from = hits)  %>% 
  select(-date)

pres_2016 <- pres_2016_results %>% 
  inner_join(select(dma, FIPS, DMA_google), by = c('county_fips' = 'FIPS')) %>%
  left_join(pres_2016_gtrend, by = c('DMA_google' = 'location')) %>%
  select(dma = DMA_google,
         fips = county_fips, 
         clinton_p, `Hilary Clinton`, trump_p, `Donald Trump`)

pres_2016 %>% ggplot(aes(x = trump_p, y = `Donald Trump`)) + geom_jitter() + geom_smooth()
pres_2016 %>% ggplot(aes(x = clinton_p, y = `Hilary Clinton`)) + geom_jitter()

pres_2020 <- pres_2020_results %>% 
  inner_join(select(dma, FIPS, DMA_google), by = c('county_fips' = 'FIPS')) %>% 
  left_join(pres_2020_gtrend, by = c('DMA_google' = 'location')) %>% 
  select(dma = DMA_google,
         fips = county_fips, 
         biden_p, `Joe Biden`, trump_p, `Donald Trump`)

pres_2020 %>% ggplot(aes(x = biden_p, y = Joe Biden`)) + geom_jitter() + geom_smooth()
pres_2020 %>% ggplot(aes(x = trump_p, y = `Donald Trump`)) + geom_jitter() + geom_smooth()

>>>>

# vacc_hes_gtrends <- find_cross_sectional_trends(c('covid conspiracy',
#                                                   'COVID-19 vaccine',
#                                                   'Coronavirus',
#                                                   'Covid-19'
#                                                   # URLdecode('%2Fg%2F11j8_9sv06'),
#                                                   # URLdecode('%2Fg%2F11j2cc_qll')
#                                                   ), 
#                             '2021-05-26', 12) %>%   
#   pivot_wider(names_from = keyword, values_from = hits)  %>% 
#   select(-date) %>% 
#   janitor::clean_names()

vacc_hes_gtrends <- read_csv(here('data', 'google_trends', 'covid19vaccinemarch3_152021.csv')) %>% 
  full_join(read_csv(here('data', 'google_trends', 'vaccinemarch3_152021.csv')), by = "DMA") %>% 
  full_join(read_csv(here('data', 'google_trends', 'Coronavirusdisease2019march3_152021.csv')), by = "DMA") %>% 
  full_join(read_csv(here('data', 'google_trends', 'Coronavirusvirusmarch3_152021.csv')), by = "DMA")  %>% 
  janitor::clean_names()  %>% 
  mutate(dma = str_to_upper(dma),
           dma = str_replace_all(dma,"-", " - "),
           dma = str_replace_all(dma,",", ""),
           dma = str_replace_all(dma,"\\s(\\w{2})\\b", " \\(\\1\\)"))

vacc_hes <- vacc_hes_data %>% 
  left_join(select(dma, FIPS, DMA_google), by = c('fips' = 'FIPS')) %>% 
  full_join(vacc_hes_gtrends, by = c('DMA_google' = 'dma'))

vacc_hes %>% 
  pivot_longer(cols = covid_19_vaccine:coronavirus_virus) %>% 
  ggplot(aes(y = vacc_hesitant, x = value, color = name)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "lm") +
  facet_wrap(~ name)

@@

# mask_gtrends <- find_cross_sectional_trends(c('Face mask',
#                                               'Mask',
#                                               'Cloth face mask'
#                                               ),
#                                             '2020-07-02', 12)%>%   
#   pivot_wider(names_from = keyword, values_from = hits)  %>% 
#   select(-date) %>% 
#   janitor::clean_names()

mask_gtrends <- read_csv(here('data', 'google_trends', 'Coronavirusdisease2019july2_142020.csv')) %>% 
  full_join(read_csv(here('data', 'google_trends', 'Coronavirusvirusjuly2_142020.csv')), by = "DMA") %>% 
    full_join(read_csv(here('data', 'google_trends', 'Cloth face mask july2_142020.csv')), by = "DMA")  %>% 
    full_join(read_csv(here('data', 'google_trends', 'mask july2_142020.csv')), by = "DMA")  %>% 
    full_join(read_csv(here('data', 'google_trends', 'Civil and political rights july2_142020.csv')), by = "DMA")  %>% 
    full_join(read_csv(here('data', 'google_trends', 'Anti-mask law july2_142020.csv')), by = "DMA")  %>% 
  janitor::clean_names()  %>% 
    mutate(dma = str_to_upper(dma),
           dma = str_replace_all(dma,"-", " - "),
           dma = str_replace_all(dma,",", ""),
           dma = str_replace_all(dma,"\\s(\\w{2})\\b", " \\(\\1\\)"))

mask <- mask_data %>% 
  left_join(select(dma, FIPS, DMA_google), by = c('fips' = 'FIPS')) %>% 
  full_join(mask_gtrends, by = c('DMA_google' = 'dma'))

mask %>% 
  pivot_longer(cols = coronavirus_disease:anti_mask_law) %>% 
  ggplot(aes(y = mask_rare, x = value, color = name)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "lm") +
  facet_wrap(~ name)

@@

append_years <- function(year_begin, year_end){
  years <- seq(year_begin,year_end,1)
  results <- tibble('location' = character(),
    # 'suicide' = numeric(), 
    # 'depression' = numeric(),
    'suicide hotline' = numeric(),
    'year' = numeric()
    )
  for (i in years){
    print(glue("finding trends for {i}..."))
    results <- find_cross_sectional_trends(c('suicide hotline'
      # 'suicide', 'depression', 
      ),
                                glue("{i}-01-01"), 365) %>%
      pivot_wider(names_from = keyword, values_from = hits)  %>%
      select(-date) %>%
      mutate(year = i) %>% 
      bind_rows(results)
  }
  results
}

hotline_gtrends <- append_years(2010, 2020)
hotline_rescale_point <-  read_csv(here('data', 'google_trends', 'suicidehotline_long_LA.csv')) %>% 
  mutate(dma = 'LOS ANGELES (CA)',
         year = as.numeric(str_sub(Month, 1, 4)),
         month = as.numeric(str_sub(Month, 6, 7)))  %>% 
  group_by(year, dma) %>%
  summarize(hits_rescale = mean(`suicide hotline`, na.rm = TRUE)) %>% 
  ungroup() %>% 
  left_join(hotline_gtrends, by = c('year' = 'year', 'dma' = 'location'))  %>% 
  mutate(rescale_ratio = hits_rescale / `suicide hotline`)  %>%
  select(year, rescale_ratio)

hotline <- hotline_gtrends %>% 
  group_by(location) %>% 
  fill( `suicide hotline`) %>%
  ungroup() %>% 
  left_join(hotline_rescale_point, by = "year") %>% 
  mutate(`suicide hotline` = `suicide hotline` * rescale_ratio) %>% 
  rename(suicide_hotline = `suicide hotline`) %>% 
  select(-rescale_ratio)

suicide <- mutate(read_csv(here('data', 'google_trends', 'suicide2010.csv')), year = 2010) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2011.csv')), year = 2011)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2012.csv')), year = 2012)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2013.csv')), year = 2013)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2014.csv')), year = 2014)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2015.csv')), year = 2015)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2016.csv')), year = 2016)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2017.csv')), year = 2017)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2018.csv')), year = 2018)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2019.csv')), year = 2019)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2020.csv')), year = 2020)) %>% 
  janitor::clean_names()

suicide_rescale_point <-  read_csv(here('data', 'google_trends', 'suicide_long_LA.csv')) %>% 
  mutate(dma = 'Los Angeles CA',
        year = as.numeric(str_sub(Month, 1, 4)),
        month = as.numeric(str_sub(Month, 6, 7)))  %>% 
  group_by(year, dma) %>%
  summarize(hits_rescale = mean(Suicide, na.rm = TRUE)) %>% 
  ungroup() %>% 
  left_join(suicide, by = c('year', 'dma'))  %>% 
  mutate(rescale_ratio = hits_rescale / suicide)  %>%
  select(year, rescale_ratio)

suicide <- suicide %>% 
    group_by(dma) %>% 
    fill(suicide) %>%
    ungroup() %>% 
    left_join(suicide_rescale_point, by = "year") %>% 
    mutate(suicide = suicide * rescale_ratio) %>% 
  select(-rescale_ratio) %>% 
  mutate(dma = str_to_upper(dma),
         dma = str_replace_all(dma,"-", " - "),
         dma = str_replace_all(dma,",", ""),
         dma = str_replace_all(dma,"\\s(\\w{2})\\b", " \\(\\1\\)"))

depression <- mutate(read_csv(here('data', 'google_trends', 'depression2010.csv')), year = 2010) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2011.csv')), year = 2011)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2012.csv')), year = 2012)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2013.csv')), year = 2013)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2014.csv')), year = 2014)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2015.csv')), year = 2015)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2016.csv')), year = 2016)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2017.csv')), year = 2017)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2018.csv')), year = 2018)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2019.csv')), year = 2019)) %>% 
  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2020.csv')), year = 2020)) %>% 
  janitor::clean_names()

depression_rescale_point <-  read_csv(here('data', 'google_trends', 'depression_long_LA.csv')) %>% 
  mutate(dma = 'Los Angeles CA',
        year = as.numeric(str_sub(Month, 1, 4)),
        month = as.numeric(str_sub(Month, 6, 7)))  %>% 
  group_by(year, dma) %>%
  summarize(hits_rescale = mean(Depression, na.rm = TRUE)) %>% 
  ungroup() %>% 
  left_join(depression, by = c('year', 'dma'))  %>% 
  mutate(rescale_ratio = hits_rescale / depression)  %>%
  select(year, rescale_ratio)

depression <- depression %>% 
    group_by(dma) %>% 
    fill(depression) %>%
    ungroup() %>% 
    left_join(depression_rescale_point, by = "year") %>% 
    mutate(depression = depression * rescale_ratio) %>% 
  select(-rescale_ratio)  %>% 
  mutate(dma = str_to_upper(dma),
         dma = str_replace_all(dma,"-", " - "),
         dma = str_replace_all(dma,",", ""),
         dma = str_replace_all(dma,"\\s(\\w{2})\\b", " \\(\\1\\)"))

suicide_data <- suicide_measures %>% 
  left_join(select(dma, FIPS, DMA_google), by = c('fips' = 'FIPS')) %>% 
  full_join(suicide, by = c('DMA_google' = 'dma', 'year' = 'year')) %>% 
  full_join(depression, by = c('DMA_google' = 'dma', 'year' = 'year')) %>% 
  full_join(hotline, by = c('DMA_google' = 'location', 'year' = 'year')) %>% 
  group_by(fips) %>%
  mutate(death_rate       = na.approx(death_rate, na.rm = FALSE),
         population       = na.approx(population, na.rm = FALSE),
         suicide          = na.approx(suicide, na.rm = FALSE),
         depression       = na.approx(depression, na.rm = FALSE),
         suicide_hotline  = na.approx(suicide_hotline, na.rm = FALSE))

@@

suicide_data <- suicide_data %>% 
  left_join(county, by = c('fips', 'year'))

write_rds(suicide_data, here('data', 'cleaned_data', 'suicide.rds'))

@@

# pres_2020_gtrend <- find_cross_sectional_trends(c('Joe Biden', 'Donald Trump'), '2020-01-01', 307) %>% 
#   pivot_wider(names_from = keyword, values_from = hits)  %>% 
#   select(-date)
pres_2020_gtrend <- read_csv(here('data', 'google_trends', 'presidents_2020.csv')) %>% 
  janitor::clean_names() %>% 
  mutate(dma = str_to_upper(dma),
         dma = str_replace_all(dma,"-", " - "),
         dma = str_replace_all(dma,",", ""),
         dma = str_replace_all(dma,"\\s(\\w{2})\\b", " \\(\\1\\)"),
         donald_trump_trend = as.numeric(str_remove(donald_trump, '%')), 
         joe_biden_trend = as.numeric(str_remove(joe_biden, '%')))

# pres_2016_gtrend <- find_cross_sectional_trends(c('Hilary Clinton', 'Donald Trump'), '2016-01-01', 307) %>%
#   pivot_wider(names_from = keyword, values_from = hits)  %>% 
#   select(-date)
pres_2016_gtrend <- read_csv(here('data', 'google_trends', 'presidents_2016.csv')) %>% 
  janitor::clean_names() %>% 
  mutate(dma = str_to_upper(dma),
         dma = str_replace_all(dma,"-", " - "),
         dma = str_replace_all(dma,",", ""),
         dma = str_replace_all(dma,"\\s(\\w{2})\\b", " \\(\\1\\)"),
         donald_trump_trend = as.numeric(str_remove(donald_trump, '%')), 
         hillary_clinton_trend = as.numeric(str_remove(hillary_clinton, '%')))

pres_2016 <- pres_2016_results %>% 
  inner_join(select(dma, FIPS, DMA_google), by = c('county_fips' = 'FIPS')) %>%
  left_join(pres_2016_gtrend, by = c('DMA_google' = 'dma')) %>%
  select(dma = DMA_google,
         fips = county_fips, 
         clinton_p, hillary_clinton_trend, trump_p, donald_trump_trend)

pres_2016 %>% ggplot(aes(x = trump_p, y = donald_trump_trend)) + geom_jitter() + geom_smooth()
pres_2016 %>% ggplot(aes(x = clinton_p, y = hillary_clinton_trend)) + geom_jitter()+ geom_smooth()

pres_2020 <- pres_2020_results %>% 
  inner_join(select(dma, FIPS, DMA_google), by = c('county_fips' = 'FIPS')) %>% 
  left_join(pres_2020_gtrend, by = c('DMA_google' = 'dma')) %>% 
  select(dma = DMA_google,
         fips = county_fips, 
         biden_p, joe_biden_trend, trump_p, donald_trump_trend)

pres_2020 %>% ggplot(aes(x = biden_p, y =joe_biden_trend)) + geom_jitter() + geom_smooth()
pres_2020 %>% ggplot(aes(x = trump_p, y = donald_trump_trend)) + geom_jitter() + geom_smooth()
